Under-approximation of Reachability in Multivalued Asynchronous Networks

### 2013-05-21 parts/sa.tex
some corrections after the reviews

The reachability of a process $a_j$ of a given sort $a$ from another process $a_i$ is called an objective and is denoted $\PHobjp{a}{j}{i}$ (\pref{def:obj}).
\begin{definition}[Objective ($\Obj$)]
\label{def:obj}
  If $a \in \components$, the reachability of a process $a_j$ from a process $a_i$ is called an \emph{objective}, noted $\PHobj{a_i}{a_j}$.
  The set of all objectives is called $\Obj \DEF \{ \PHobj{a_i}{a_j} \mid a \in \components \wedge (a_i, a_j) \in \PHl_a^2 \}$.
  For an objective $P = \PHobj{a_i}{a_j} \in \Obj$, we define: $\PHsort(P) = a$, $\PHtarget(P)=a_i$, $\PHbounce(P)=a_j$,
  and $P$ is \emph{trivial} if $a_i = a_j$.

@@

A context (\pref{def:context}) extends the notion of state to a set of possible initial states.
We also extend the override operator to contexts (\pref{def:ctxcap}).
\begin{definition}[Context ($\Ctx$)]
\label{def:context}
  A \emph{context} $\ctx$ associates to each sort in $\PHs$ a non-empty subset of its processes:
  $\forall a \in \PHs, \PHget{\ctx}{a} \subseteq \PHl_a \wedge \PHget{\ctx}{a} \neq \emptyset$.
  $\Ctx$ is the set of all contexts.
\end{definition}
%
\begin{definition}[$\Cap: \Ctx \times \powerset(\PHproc) \rightarrow \Ctx$]
\label{def:ctxcap}
  For any $\ctx\in\Ctx$ and set of processes $ps \in \powerset(\PHproc)$,
  the override of $\ctx$ by $ps$ is noted $\ctx \Cap ps$ and is defined by:
  \[ \forall a \in \PHs, \PHget{(\ctx \Cap ps)}{a} =
  \begin{cases}
    \{ p \in ps \mid \PHsort(p)=a \} & \text{if } \exists p \in ps, \PHsort(p)=a,\\
    \PHget{\ctx}{a} & \text{else.}
  \end{cases}
  \]
\end{definition}
\noindent
For a given context $\ctx$, we note $a_i \in \ctx$ if and only if $a_i \in \PHget{\ctx}{a}$,
and for all $ps \in \powerset(\PHproc)$ or $ps \in \PHl$, $ps \subseteq \ctx \EQDEF \forall a_i \in ps, a_i \in \ctx$.
A sequence of actions $\delta$ is \emph{playable} in a context $\ctx$ if and only if 
$\exists s \subseteq \ctx, \delta \in \Sce(s)$.
We denote then: $\delta \in \Sce(\ctx)$,
and the play of $\delta$ in $\ctx$ is $\ctx \PHplay \delta = \ctx \Cap \ceil(\delta)$,
where $\ceil(\delta)$ is the set containing the last process (hitter or bounce) of each sort present in $\delta$.

Finally, a bounce sequence on a sort $a$ (\pref{def:bs}) is a sequence of actions hitting $a$
in which the bounce process of each action is the hitter process of the following action.
Bounce sequences are used to find local solutions to a given objective.
A bounce sequence can be abstracted into sets of all its hitters that are not in sort $a$.
This abstraction allows to propagate an objective into objectives on other sots.
In the following, we denote: $\Sol = \powerset(\PHproc)$.
\begin{definition}[Bounce sequence ($\BS$)]
\label{def:bs}
  A \emph{bounce sequence} $\zeta$ is a sequence of actions so that $\forall n \in \indexes{\zeta}, n < |\zeta|, \PHbounce(\zeta_{n}) = \PHtarget(\zeta_{n+1})$.
  $\BS$ denotes the set of all bounce sequences, and
  $\BS(P)$ denotes the set of bounce sequences \emph{solving} an objective $P$:
  \[
    \BS(\PHobj{a_i}{a_j}) = \{ \zeta \in \BS \mid \PHtarget(\zeta_1)= a_i \wedge \PHbounce(\zeta_{|\zeta|}) = a_j \} \enspace.
  \]
  $\BS(\obj{a_i}{a_j}) = \emptyset$ if there is no way to reach $a_j$ from $a_i$ and $\emptyseq \in \BS(\obj{a_i}{a_i})$.
\end{definition}
%
\begin{definition}[$\aBS:\Obj \rightarrow \powerset(\Sol)$]
\label{def:aBS}
  \[
    \aBS(P) = \{ \abstr{\zeta} \in \Sol \mid \zeta \in \BS(P), \nexists \zeta' \in \BS(P), \abstr{\zeta'} \subsetneq \abstr{\zeta} \} \enspace,
  \]
  where $\abstr{\zeta} = \{ \PHhitter(\zeta_n) \mid  n \in \indexes{\zeta} \wedge \PHsort(\PHhitter(\zeta_n)) \neq \PHsort(P) \}$.
\end{definition}

@@

For any objective $P$ and context $\ctx$, \pref{def:maxCont} allows to obtain the set of processes of sort $\PHsort(P)$ are required to solve $P$ in $\ctx$, given by $\gCont_\ctx(\PHsort(P), P)$.
\begin{definition}[$\gCont_\ctx : \Sigma \times \Obj \rightarrow \powerset(\PHproc)$]
  \label{def:maxCont}
  \begin{align*}
    \gCont_\ctx(a,P) = 
    \{ p \in \PHproc &\mid \exists ps \in \aBS(P), \exists b_i \in ps, b = a \wedge p = b_i \\
      & \vee b \neq a \wedge p \in \gCont_\ctx(a, \PHobj{b_j}{b_i}) \wedge b_j \in \PHget{\ctx}{b} \}
    \enspace.
  \end{align*}
\end{definition}

The graph of local causality $\cwB = (\V, \E)$ defined in \pref{def:glc} is a graph where $\V \subset \Proc \cup \Obj \cup \Sol$ and $\E \subset \V \times \V$.
A node in $\PHproc$ is a required process,
a node in $\Obj$ is an objective to reach a given process
and a node in $\Sol$ is a set of processes required for the solving.
An objective $P \in \Obj$ is solvable if the abstractions of bounce sequences $\aBS(P) \in \Sol$ (\pref{def:aBS}) can be reached (\pref{eq:ESol1}), thus leading to several required processes (\pref{eq:ESol2}).
If $a \in \components$, the reachability of one of its process $a_i$ is approximated by the ability to solve all objectives $\PHobjp{a}{j}{i} \in \Obj$ for all $a_j$ in the initial context (\pref{eq:EReq});
if $a \in \cs$, the reachability of $a_i$ is simply solved by the set of processes $\csState(a_i)$ (\pref{def:csState}) that it represents (\pref{eq:EPrio}).
The solving of an objective $P$ may require a process of $\PHsort(P)$, \ie $\gCont(\PHsort(P), P) \neq \emptyset$ (\pref{def:maxCont}); in this case, $P$ is re-targeted (\pref{eq:ECont}).
\pref{eq:Vw}, \eqref{eq:Vproc} and~\eqref{eq:VE} ensure that all required nodes are in $\cwV$.
Finally, as the active process of every sort may evolve, $\cwB$ is obtained by iteratively saturating with every process it contains,
\ie by overriding its initial context $\ctx$ by $\allprocs(\V, \E)$, defined by:
$$\allprocs(\V, \E) = (V \cap \Proc) \cup \{ \PHtarget(P), \PHbounce(P) \mid P \in \V \cap \Obj \}$$

@@

\begin{definition}
\label{def:glc}
  The graph of local causality $\cwB = (\Bv, \Be)$ is defined as: $\cwB = \lfp{\aB^\w_\ctx}{\myB}{\aB^\w_{\ctx \Cap \allprocs(\myB)}}$,
  where $\myB = (\cwV, \cwE)$ is the smallest graph with
  $\cwV \subset \Proc \cup \Obj \cup \Sol$ and $\cwE \subset \cwV \times \cwV$
  so that:
  \begin{align}
    \w &\subset \cwV \label{eq:Vw} \\
    P \in \VProc &\Rightarrow \PHbounce(P) \in \cwV \label{eq:Vproc} \\
    (x, y) \in \E &\Rightarrow y \in \cwV \label{eq:VE} \\
    P \in \VObj \wedge ps \in \BS(P) &\Rightarrow (P, ps) \in \cwE \label{eq:ESol1} \\
    ps \in \VSol \wedge a_i \in ps &\Rightarrow (ps, a_i) \in \cwE \label{eq:ESol2} \\
    a \in \components \wedge a_i \in \VProc \wedge a_j \in \ctx &\Rightarrow (a_i, \PHobjp{a}{j}{i}) \in \cwE \label{eq:EReq} \\
    a \in \cs \wedge a_i \in \VProc \wedge ps \in \csState(a_i) &\Rightarrow (a_i, ps) \in \cwE \label{eq:EPrio} \\
    P \in \VObj \wedge q \in \gCont_\ctx(\PHsort(P), P) &\Rightarrow (P, \PHobj{q}{\PHbounce(P)}) \in \cwE \label{eq:ECont}
  \end{align}
\end{definition}

@@

In the graph of local causality, an edge $(p, ps) \in \Proc \times \Sol$ %linking a process of a cooperative sort to a solution set $ps$
is said coherent (\pref{def:coherent}) if none of the processes in $ps$ conflict with the children processes of $ps$.
Then, \pref{th:approxinf} gives a sufficient condition for the concretization of a sequence of objectives in a given context,
which is derived immediately from the graph of local causality.
A proof of this theorem is given in Annex~\ref{suppl:demoapproxinf}.
\begin{definition}[Coherent edge]
\label{def:coherent}
  An edge $(x, y) \in \cwE$ is said coherent if and only if:
  $(x, y) \in \Be \cap (\Proc \times \Sol) \Rightarrow y$ has no children process $a_j \in \Bv \cap \Proc$ so that $\exists a_i \in y$, $a_i \neq a_k$.
\end{definition}

@@

    \node[Aproc,below of=c01s] (ab11) {$ab_{11}$};
    \node[AsolPrio,below of=ab11] (ab11s) {};

@@

    \path
    (c1) edge (c01)
    (c01) edge (c01s)
    (c01s) edge (ab11)
    (ab11) edge (ab11s)
    (ab11s) edge (a1) edge (b1)

@@

    (b0) edge (b10) edge (b00)
    (b10) edge (b10s)
    (b00) edge (b00s)
    (b1) edge (b01) edge (b11)
    (b01) edge (b01s)
    (b01s) edge (a0)
    (b11) edge (b11s)
    ;
    \end{tikzpicture}
  \caption{
  \label{fig:sa-livelock}
    The graph of local causality of the PH model in \pref{fig:ph-livelock}.
    \pref{th:approxinf} is inconclusive on this example as the only solution of process $ab_{11}$ is not coherent (\pref{def:coherent}).
  }
\end{figure}

@@

It is also possible to compute the reachability of a set of states $S \subset \PHl$ by creating several actions $\PHhit{\total_s}{\reach_0}{\reach_1}$ in $\PHh^{(2)}$ for each state $s \in S$.

>>>>

The reachability of a process $a_j$ of a given sort $a$ from another process $a_i$ is called an objective and is denoted $\PHobjp{a}{i}{j}$ (\pref{def:obj}).
\begin{definition}[Objective ($\Obj$)]
\label{def:obj}
  If $a \in \components$, the reachability of a process $a_j$ from a process $a_i$ is called an \emph{objective}, noted $\PHobj{a_i}{a_j}$.
  The set of all objectives is called $\Obj \DEF \{ \PHobj{a_i}{a_j} \mid a \in \components \wedge (a_i, a_j) \in \PHl_a^2 \}$.
  For an objective $P = \PHobj{a_i}{a_j} \in \Obj$, we define: $\PHsort(P) = a$, $\PHtarget(P)=a_i$, $\PHbounce(P)=a_j$,
  and $P$ is said \emph{trivial} if $a_i = a_j$.

@@

A context (\pref{def:context}) extends the notion of state to a set of possible initial states.
We also extend the override operator to contexts (\pref{def:ctxcap}).
\begin{definition}[Context ($\Ctx$)]
\label{def:context}
  A \emph{context} $\ctx$ associates to each sort in $\PHs$ a non-empty subset of its processes:
  $\forall a \in \PHs, \PHget{\ctx}{a} \subseteq \PHl_a \wedge \PHget{\ctx}{a} \neq \emptyset$.
  $\Ctx$ is the set of all contexts.
\end{definition}
%
\begin{definition}[$\Cap: \Ctx \times \powerset(\PHproc) \rightarrow \Ctx$]
\label{def:ctxcap}
  For any $\ctx\in\Ctx$ and set of processes $ps \in \powerset(\PHproc)$,
  the override of $\ctx$ by $ps$ is noted $\ctx \Cap ps$ and is defined by:
  \[ \forall a \in \PHs, \PHget{(\ctx \Cap ps)}{a} =
  \begin{cases}
    \{ p \in ps \mid \PHsort(p)=a \} & \text{if } \exists p \in ps, \PHsort(p)=a,\\
    \PHget{\ctx}{a} & \text{else.}
  \end{cases}
  \]
\end{definition}
\noindent
For a given context $\ctx$, we note $a_i \in \ctx$ if and only if $a_i \in \PHget{\ctx}{a}$,
and for all $ps \in \powerset(\PHproc)$ or $ps \in \PHl$, $ps \subseteq \ctx \EQDEF \forall a_i \in ps, a_i \in \ctx$.
A sequence of actions $\delta$ is \emph{playable} in a context $\ctx$ if and only if 
$\exists s \subseteq \ctx, \delta \in \Sce(s)$.
We denote then: $\delta \in \Sce(\ctx)$,
and the play of $\delta$ in $\ctx$ is $\ctx \PHplay \delta = \ctx \Cap \ceil(\delta)$,
where $\ceil(\delta)$ is the set containing the last process in the sequence $\delta$ (hitter or bounce) of every sort mentioned in $\delta$.

Finally, a bounce sequence on a sort $a$ (\pref{def:bs}) is a sequence of actions hitting $a$
in which the bounce process of each action is the hitter process of the following action.
Bounce sequences are used to find local solutions to a given objective.
A bounce sequence on $a$ can be abstracted into sets of all its hitters that are not in sort $a$ (\pref{def:aBS}).
This abstraction allows to propagate an objective on the sort $a$ into objectives on other sots.
In the following, we denote: $\Sol = \powerset(\PHproc)$.
\begin{definition}[Bounce sequence ($\BS$)]
\label{def:bs}
  A \emph{bounce sequence} $\zeta$ is a sequence of actions so that $\forall n \in \indexes{\zeta}, n < |\zeta|, \PHbounce(\zeta_{n}) = \PHtarget(\zeta_{n+1})$.
  $\BS$ denotes the set of all bounce sequences, and
  $\BS(P)$ denotes the set of bounce sequences \emph{solving} an objective $P$:
  \[
    \BS(\PHobj{a_i}{a_j}) = \{ \zeta \in \BS \mid \PHtarget(\zeta_1)= a_i \wedge \PHbounce(\zeta_{|\zeta|}) = a_j \} \enspace.
  \]
  $\BS(\obj{a_i}{a_j}) = \emptyset$ if there is no way to reach $a_j$ from $a_i$ and $\emptyseq \in \BS(\obj{a_i}{a_i})$.
\end{definition}
%
\begin{definition}[$\aBS:\Obj \rightarrow \powerset(\Sol)$]
\label{def:aBS}
  The \emph{abstractions of bounce sequences} of an objective $P$, denoted by the set $\aBS(P)$, are the sets of hitters of bounce sequences solving $P$:
  \[
    \aBS(P) = \{ \abstr{\zeta} \in \Sol \mid \zeta \in \BS(P), \nexists \zeta' \in \BS(P), \abstr{\zeta'} \subsetneq \abstr{\zeta} \} \enspace,
  \]
  where $\abstr{\zeta} = \{ \PHhitter(\zeta_n) \mid  n \in \indexes{\zeta} \wedge \PHsort(\PHhitter(\zeta_n)) \neq \PHsort(P) \}$.
\end{definition}

@@

For any objective $P$ and context $\ctx$, \pref{def:maxCont} allows to obtain the set of processes of sort $\PHsort(P)$ that are required to solve $P$ in $\ctx$, given by $\gCont_\ctx(\PHsort(P), P)$.
\begin{definition}[$\gCont_\ctx : \Sigma \times \Obj \rightarrow \powerset(\PHproc)$]
  \label{def:maxCont}
  \begin{align*}
    \gCont_\ctx(a,P) = 
    \{ p \in \PHproc &\mid \exists ps \in \aBS(P), \exists b_i \in ps, b = a \wedge p = b_i \\
      & \vee b \neq a \wedge p \in \gCont_\ctx(a, \PHobj{b_j}{b_i}) \wedge b_j \in \PHget{\ctx}{b} \}
    \enspace.
  \end{align*}
\end{definition}

The graph of local causality $\cwB = (\V, \E)$ defined in \pref{def:glc} is a graph where $\V \subseteq \Proc \cup \Obj \cup \Sol$ and $\E \subseteq \V \times \V$.
A node in $\PHproc$ is a required process,
a node in $\Obj$ is an objective to reach a given process
and a node in $\Sol$ is a set of processes required for the solving.
An objective $P \in \Obj$ is solvable if the abstractions of bounce sequences $\aBS(P) \in \Sol$ (\pref{def:aBS}) can be reached (\pref{eq:ESol1}), thus leading to several required processes (\pref{eq:ESol2}).
If $a \in \components$, the reachability of one of its process $a_i$ is approximated by the ability to solve all objectives $\PHobjp{a}{j}{i} \in \Obj$ for all $a_j$ in the initial context (\pref{eq:EReq});
if $a \in \cs$, the reachability of $a_i$ is simply solved by the set of processes $\csState(a_i)$ (\pref{def:csState}) that it represents (\pref{eq:EPrio}).
The solving of an objective $P$ may require a process of $\PHsort(P)$, \ie $\gCont(\PHsort(P), P) \neq \emptyset$ (\pref{def:maxCont}); in this case, $P$ is re-targeted (\pref{eq:ECont}).
\pref{eq:Vw}, \eqref{eq:Vproc} and~\eqref{eq:VE} ensure that all required nodes are in $\cwV$.
Finally, as the active process of every sort may evolve, $\cwB$ is obtained by iteratively saturating with every process it contains,
\ie by overriding its initial context $\ctx$ by $\allprocs(\V, \E)$, defined by:
$$\allprocs(\V, \E) = (V \cap \Proc) \cup \{ \PHtarget(P), \PHbounce(P) \mid P \in \V \cap \Obj \}$$

@@

\begin{definition}
\label{def:glc}
  The graph of local causality $\cwB = (\Bv, \Be)$ is defined as: $\cwB = \lfp{\aB^\w_\ctx}{\myB}{\aB^\w_{\ctx \Cap \allprocs(\myB)}}$,
  where $\myB = (\cwV, \cwE)$ is the smallest graph with
  $\cwV \subseteq \Proc \cup \Obj \cup \Sol$ and $\cwE \subseteq \cwV \times \cwV$
  so that:
  \begin{align}
    \w &\subseteq \cwV \label{eq:Vw} \\
    P \in \VProc &\Rightarrow \PHbounce(P) \in \cwV \label{eq:Vproc} \\
    (x, y) \in \E &\Rightarrow y \in \cwV \label{eq:VE} \\
    P \in \VObj \wedge ps \in \BS(P) &\Rightarrow (P, ps) \in \cwE \label{eq:ESol1} \\
    ps \in \VSol \wedge a_i \in ps &\Rightarrow (ps, a_i) \in \cwE \label{eq:ESol2} \\
    a \in \components \wedge a_i \in \VProc \wedge a_j \in \ctx &\Rightarrow (a_i, \PHobjp{a}{j}{i}) \in \cwE \label{eq:EReq} \\
    a \in \cs \wedge a_i \in \VProc \wedge ps \in \csState(a_i) &\Rightarrow (a_i, ps) \in \cwE \label{eq:EPrio} \\
    P \in \VObj \wedge q \in \gCont_\ctx(\PHsort(P), P) &\Rightarrow (P, \PHobj{q}{\PHbounce(P)}) \in \cwE \label{eq:ECont} \!
  \end{align}
\end{definition}

@@

In the graph of local causality, an edge $(p, ps) \in \Proc \times \Sol$ %linking a process of a cooperative sort to a solution set $ps$
is said coherent (\pref{def:coherent}) if none of the processes in $ps$ conflict with the children processes of $ps$.
Then, \pref{th:approxinf} gives a sufficient condition for the concretization of a sequence of objectives in a given context,
which is derived immediately from the graph of local causality.
A proof of this theorem is given in Annex~\ref{suppl:demoapproxinf}.
\begin{definition}[Coherent edge]
\label{def:coherent}
  An edge $(x, y) \in \cwE$ is said coherent if and only if:
  $(x, y) \in \Be \cap (\Proc \times \Sol) \Rightarrow y$ has no children process $a_j \in \Bv \cap \Proc$ so that $\exists a_i \in y$, $a_i \neq a_j$.
\end{definition}

@@

    \node[AprocPrio,below of=c01s] (ab11) {$ab_{11}$};
    \node[AsolPrio,below of=ab11] (ab11s) {};

@@

    \path
    (c1) edge (c01)
    (c01) edge (c01s)
    (c01s) edge (ab11)
    (ab11) edge[aSPrio] (ab11s)
    (ab11s) edge (a1) edge (b1)

@@

    (b0) edge (b10) edge (b00)
    (b10) edge (b10s)
    (b00) edge (b00s)
    (b1) edge (b01) edge (b11)
    (b01) edge (b01s)
    (b01s) edge (a0)
    (b11) edge (b11s)
    ;
    \end{tikzpicture}
  \caption{
  \label{fig:sa-livelock}
    The graph of local causality of the PH model in \pref{fig:ph-livelock}.
    Rectangular nodes containing a single process are elements in $\Proc$,
    nodes containing a couple of processes are elements in $\Obj$
    and circle nodes are elements in $\Sol$.
    %The double arrow and the two surrounding nodes represent the only edge in $\Proc \times \Sol$.
    \pref{th:approxinf} is inconclusive on this example as edge $(ab_{11}, \{ a_1, b_1 \}) \in \Proc \times \Sol$ (here represented with a double line) is not coherent (\pref{def:coherent}).
    Indeed, $a_0 \in \Proc$ is a child of $\{ a_1, b_1 \}$, but $a_0 \neq a_1$ (and the same also stands for $b_0$).
  }
\end{figure}

@@

It is also possible to compute the reachability of a set of states $S \subseteq \PHl$ by creating several actions $\PHhit{\total_s}{\reach_0}{\reach_1}$ in $\PHh^{(2)}$ for each state $s \in S$.

### 2013-05-21 parts/suppl-ph-dn.tex
several fixes; first final version
some corrections after the reviews

\section{Weak Bisimulation of Asynchronous Discrete Networks}
\label{suppl:demotrad}

@@

A Discrete Network gathers a finite number of components $i\in\segm{1}{n}$ having a discrete finite domain
$\mathbb F^i$ that we note $\mathbb{F}^i = \segm{1}{l_i}$.
For each component $i\in\segm{1}{n}$, a map $\mathbb F \mapsto \mathbb F^i$ is defined, where
$\mathbb F = \mathbb F^1 \times \cdots \times \mathbb F^n$, giving the next value of the component
with respect to the global state of the network.
Typically $f^i$ depends on a subset of components that we denote $\DNdep(f^i)$.
In the case of Asynchronous Discrete Networks (ADN), a transition relation $\DNtrans\subset \mathbb
F\times \mathbb F$ is defined such that $x\DNtrans x'$ if and only if there exists a unique
$i\in\segm{1}{n}$ such that $\get{x'}{i}=f^i(x)$ and $\forall j\in\segm{1}{n}, j\neq i, \get{x'}{j}
=\get{x}{j}$, i.e.~one and only one component has been updated.
This is formalised in \pref{def:DN}.

>>>>

\section{Weak Bisimulation of Asynchronous Discrete Networks (\pref{ssec:hypothesis})}
\label{suppl:demotrad}

@@

A Discrete Network gathers a finite number of components $i\in\segm{1}{n}$ having a discrete finite domain
$\mathbb F^i$ that we note $\mathbb{F}^i = \segm{1}{l_i}$.
For each component $i\in\segm{1}{n}$, a map $\mathbb F \mapsto \mathbb F^i$ is defined, where
$\mathbb F = \mathbb F^1 \times \cdots \times \mathbb F^n$, giving the next value of the component
with respect to the global state of the network.
Typically $f^i$ depends on a subset of components that we denote $\DNdep(f^i)$.
In the case of Asynchronous Discrete Networks (ADN), a transition relation $\DNtrans\subseteq \mathbb
F\times \mathbb F$ is defined such that $x\DNtrans x'$ if and only if there exists a unique
$i\in\segm{1}{n}$ such that $\get{x'}{i}=f^i(x)$ and $\forall j\in\segm{1}{n}, j\neq i, \get{x'}{j}
=\get{x}{j}$, i.e.~one and only one component has been updated.
This is formalised in \pref{def:DN}.
